% LaTeX file for resume
% This file uses the resume document class (res.cls)

\documentclass[margin]{res}
% the margin option causes section titles to appear to the left of body text
\textwidth=5.2in % increase textwidth to get smaller right margin
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\usepackage{hyperref}
\setlength{\parskip}{0pt}
\setlength{\parsep}{0pt}

\begin{document}

\name{Ami Patel\\[0pt]} % the \\[12pt] adds a blank line after name

\address{ \textbf{Phone}:\hspace{1mm}\href{+1-669-251-5680}{+1-669-251-5680}\hspace{5mm} \textbf{Github}:\hspace{1mm}\href{https://github.com/amiforgit}{amiforgit}\hspace{5mm}      \textbf{Email}:\hspace{1mm}\href{mailto:ami.patel317@gmail.com}{ami.patel317@gmail.com} }

\begin{resume}


\section{Objective }

  Seeking an internship in Software Engineering in an organization where I can con-tribute towards its growth using my technical background and experience.
  
\section{Interests}

  Full stack web development, Mobile app development and Machine Learning

\section{Education}
  Masters in Software Engineering \\
  \vspace{1.5mm}
  {\bf San Jose State University}, August 2016 - May 2018(Expected Graduation) \\ 
   Bachelors in Engineering in Computer Engineering \\
   \vspace{1.5mm}
  {\bf  L.D College of Engineering}, 2012 - 2016 {\bf (CG 3.71/4.0) } \\
  
\section{Skill Set}
   \begin{tabular}{l p{3in}}
    {\bf Programming:} & JAVA, Python, PHP, C, Objective C \\
    {\bf Databases:} & MYSQL, MongoDB, SQLite , RDS  \\
    {\bf Web Technologies:} &  HTML5, CSS 3.0, JavaScript, Node.js \\
    {\bf Cloud Technologies:} &  AWS, Google App Engine \\
    \bf {Dev Tools:} & Eclipse, IntelliJ, Git \\
    {\bf Testing Tools:} & Junit\\
    {\bf Other:} & Docker,Linux, Android, Scrum \\
     \end{tabular}

\section{Experience}

 
 {\bf Software Engineer Intern,} SoftVan Technologies, \hfill June  2015  - May 2016
 \begin{itemize} \itemsep -1pt  % reduce space between items
 \item Contributed in all phases of SDLC from requirements gathering to maintenance.
  \item Build a website in a team of 2 as part of demo for Smart City Project, designed user interface, database models and integrated with app using web services.
\end{itemize}
 
\section{Academic Projects}
 
 {\bf Smart Travel System }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Implemented functionality for navigation, searching and reviewing of various places, feedback processing, image upload and display, fare estimation using Java and MySQL. Generated graphs for the data stored.
 \item  Google Maps API for providing navigation facilities to user.
 \end{itemize}
 
 {\bf Mobile Sensor Cloud Infrastructure as a Service }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developed a Mobile Sensor Iaas  using  AWS, Java, MySQL, HTML, CSS.
 \item Comprised cloud components like Scalability, Load-balancing, Dashboard
 \end{itemize}
 
 {\bf Cross Domain Online Market Place}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item A market place having websites created by each team member and counting the number of visits and giving suggestions based on it along with user tracking using PHP, MySQL and Heroku.
 \item Created rich UI using HTML5, CSS, JavaScript and Bootstrap 
 \end{itemize}

 {\bf Identity Checker using Face Recognition }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Algorithm that checks the matching percentage of live image uploaded using camera or mobile device against the one in database by use of TensorFlow and Python
 \item Used Android for providing user interface
 \end{itemize}
 
 \section{Hobby Projects}
 
 {\bf Mortgage Calculator }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Built an Android App that takes the information of a certain property along with the loan information and calculates monthly mortgage. 
 \item Performed address validation using Google Maps API.
 \end{itemize}
 
{\bf Sort It Out }
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item A rich-UI multi-player game based on quick sort and selection sort using Java in Greenfoot. Also, used Amazon AWS 
 \item The team followed Scrum and Kanban practices during the development 
 \end{itemize}
\section{Publications}
 
 {\bf A Comprehensive Study on Mobile Sensing and Cloud Services }
 \begin{itemize} \itemsep -2pt  % reduce space between items
\item Wrote a survey paper on Monitoring, Billing, Management and Virtualization of mobile sensor network.
  \end{itemize}
 

 
\section{Other}
 Volunteer at Silicon Valley Code Camp and ISO-SJSU.\\
 Regularly solving data structures problems at leetcode. \\

\end{resume}
\end{document}